No Evidence for the Aquarius Co-Moving Group \\Resulting from a Disrupted Classical Globular Cluster\altaffilmark{1}

### 2013-01-30 2012-aqs/draft-aqs.tex
yolo

\usepackage{amssymb,graphics} % for resolution symbol

@@

% TODO:
% [DONE] Na/O subplots
% Na/O comparison with halo
% [DONE] Mg/Al subplots
% - Ni/Na plane plot
% - Add standard stars to observations table
% - Add standard stars chemical abundances
% - Add in-line text referencing standard star chemical abundances
% - Uncertainties analysis
% - Strontium?
% - Carbon?
% - Distance calculations
% - Transverse motions table
% - Transverse motions text
% - Orbital energies plot
% - Minor merger text
% - Conclusions

% Casey, Keller, Alves-Brito, Frebel, Da Costa, Schlaufman, Freeman, Heather, QinQin

@@

Wide-field surveys have proved excellent sources for finding stellar streams. Dozens have been identified through photometric selections and metched-filtering techniques, with some to a galactocentric distance of 100\,kpc \citep{belokurov;et-al_2007,koposov_SG1, drake;et-al_2013}. Indeed, it is clear that a large fraction of the stellar halo has been built up by accretion. However, as \citet{helmi;white_1999} point out, these observing strategies are only successful for identifying streams that are sufficiently distant from the solar neighbourhood. A nearby stream, within $\sim$10\,kpc, will not appear as an over-density, as the stars would be sparsely positioned across the sky. Such substructures would only be detectable by their kinematics, or perhaps precise chemical abundances through a `chemical tagging' approach (e.g. see \citet{freeman;bland-hawthorn_2003}).

% Talk about RAVE
It is therefore necessary to survey solar neighbourhood stars with spectroscopy to permit any nearby substructures to reveal themselves. The RAVE (Radial Velocity Experiment) team began such a survey in 2003 and have observed spectra from over 500,000 stars across 17,000\,deg$^{2}$. As the name hints, the primary goal of RAVE was to obtain radial velocities for the solar neighbourhood and beyond. In an attempt to remain kinematically unbiased, RAVE candidates were selected based only on their apparent magnitude. With the exception of bulge stars, where some photometric cuts were employed, all stars between 9 $<$ I $<$ 13 were observed. Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with sufficient Signal-to-Noise ($S/N$), estimates of stellar parameters have been derived using a $\chi^2$ minimization technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.

@@

We seek to investigate the nature of the Aquarius stream, specifically the recent globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}. We present a detailed analysis for five Aquarius stream candidates from high-resolution, high $S/N$ observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{bernstein;et-al_2003} with the Magellan Clay telescope. Details of the observations and data reduction are outlined in the following section. The data analysis is chronicled in Section \ref{sec:analysis} and a detailed discussion of these results resides in Section \ref{sec:discussion}. In Section \ref{sec:conclusion} we present our conclusions and critical interpretations.

@@

C2225316-14437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 1.033 & \dots & \dots & 135	 & --168.6	& --156.4 & 0.1 \\
C2306265-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 1.096 & \dots & \dots & 100	 & --240.4	& --221.1 & 0.1 \\
HD41667			& 06:05:03.7 & $-$32:59:36.8	& 2011-03-13	& 1.005	& \dots & \dots & \dots & 314.4	& \dots & 0.8 \\
HD142948		& 16:00:01.6 & $-$53:51:04.1	& 2011-03-14	& 1.107	& \dots & \dots & \dots & 6.8		& \dots & 0.4 \\
J221821-183424	& 22:18:21.2 & $-$18:34:28.3	& 2011-07-30	& 1.026	& \dots & \dots & 115 	 & --170.2	& --159.5 & 0.1 \\
J223504-152834	& 22:35:04.5 & $-$15:28:34.9	& 2011-07-30	& 1.047	& \dots & \dots & 135	 & --179.0	& --169.7 & 0.1 \\
J223811-104126	& 22:38:11.6 & $-$10:41:29.4	& 2011-07-30	& 1.218	& \dots & \dots & 115	 & --250.1	& --235.7 & 0.1

@@

The most complete sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}. Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional candidate from the original \citet{williams;et-al_2011} sample. The supplementary star, J2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined. All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and X additional standard stars were observed in March 2011. All observations were taken using a 1.0'' slit, providing a spectral resolution of $\mathcal{R} = 28,000$ in the blue and $\mathcal{R} = 22,000$ in the red arm. The total exposure times for our program stars varied per star from X-Y seconds to ensure a $S/N$ ratio in excess of 100\,pixel$^{-1}$ at 600\,nm.

@@

The white dwarf HR 6141 was observed on X as a telluric standard. The $S/N$ ratio for HR 6141 exceeds that in any of our standard or program stars. Although the atmospheric conditions at Las Campanas Observatory are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify lines that are affected by telluric absorption. Critical transitions necessary for abundance analyses that are affected by the earth's atmosphere are corrected for telluric absorption (see \S\ref{sec:telluric-absorption}).

@@

\subsection{Radial Velocities}
\label{sec:radial-velocities}
The radial velocity for each star was determined in a two-step method. An initial estimate of the radial velocity was ascertained by cross-correlation with a synthetic spectrum of a giant star with $T_{\rm eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}. The observed spectrum was shifted to the pseudo-rest frame using this initial velocity estimate. Velocities found from cross-correlation are typically within 1\,km\,s$^{-1}$ of our final published value.

@@

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/line-velocity.pdf}
	\caption{Residual velocities for each absorption line with a well-fitted Gaussian profile after correcting for doppler shift using the initial cross-correlation measurement. The mean residual velocity $-0.75$\,km\,s$^{-1}$ is within the 1-$\sigma$ cross-correlation uncertainty of $\pm0.9$\,km\,s$^{-1}$.}
	\label{fig:line-velocities}
\end{figure}

@@

We list the atomic data and measured equivalent widths for transitions used during this analysis in Table \ref{tab:equivalent-widths}. Saturated lines were excluded by removing measurements with reduced equivalent widths, $\log_{10}{(EW/\lambda)} > -4.5$\, dex. A minimum detectable equivalent width was calculated as a function of wavelength based on the $S/N$, and only lines that exceeded a 3-$\sigma$ detection significance were included. We have verified the approach by comparing our measurements of 156 lines in HD 140283 with the study of \citet{norris;et-al_1996}. We only included measurements in the \citet{norris;et-al_1996} study that were not marked with questionable line quality parameters. Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}. The mean difference is a negligible $-0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present. We note that the scatter may be directly attributed to the observed $S/N$ ratio, as other studies using the same equivalent width measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ratios ($0.20 \pm 0.16$\,m{\AA} with $S/N \sim X$, $0.25 \pm 0.28$\,m{\AA} with $S/N \sim{} Y$; \citet{frebel;et-al_2013}).

@@

\tablecolumns{1}

@@

 6300.300 &       8.0 &      0.00 &    --9.717 &     45.37 &     66.93 &     38.48 &     32.85 &     17.87 \\
 6363.780 &       8.0 &      0.02 &   --10.185 &     19.47 &     28.31 &     12.96 &     18.83 &   \nodata \\
 5688.190 &      11.0 &      2.11 &    --0.420 &   \nodata &   \nodata &     48.97 &    131.49 &     38.41 \\
 6154.230 &      11.0 &      2.10 &    --1.530 &     24.06 &     38.89 &   \nodata &     48.49 &   \nodata \\
 6160.750 &      11.0 &      2.10 &    --1.230 &     37.72 &     58.49 &   \nodata &     65.72 &   \nodata \\
 6318.720 &      12.0 &      5.11 &    --1.970 &   \nodata &     47.94 &     14.69 &     62.79 &      8.88 \\
 6319.240 &      12.0 &      5.11 &    --2.220 &     30.84 &   \nodata &      5.51 &   \nodata &   \nodata \\
 6965.410 &      12.0 &      5.75 &    --1.510 &   \nodata &   \nodata &   \nodata &     59.22 &   \nodata \\
 7387.690 &      12.0 &      5.75 &    --0.870 &     51.71 &     56.30 &     24.68 &     76.01 &     23.99 \\
 6696.020 &      13.0 &      3.14 &    --1.340 &     72.83 &     63.60 &     12.99 &   \nodata &   \nodata \\
 6698.670 &      13.0 &      3.14 &    --1.640 &     39.67 &     33.44 &   \nodata &     39.50 &   \nodata \\
 7835.310 &      13.0 &      4.02 &    --0.470 &     47.77 &     38.44 &   \nodata &     55.91 &      5.39 \\
 7836.130 &      13.0 &      4.02 &    --0.310 &     62.78 &     44.72 &   \nodata &     69.13 &     13.23 \\
 5690.430 &      14.0 &      4.93 &    --1.751 &     56.17 &     43.76 &     25.75 &     53.45 &     16.77 \\
 5793.070 &      14.0 &      4.93 &    --1.843 &     46.13 &     39.81 &     19.33 &     48.39 &   \nodata \\
 6125.020 &      14.0 &      5.61 &    --1.506 &     40.93 &     23.45 &     10.86 &     34.74 &   \nodata \\
 6145.010 &      14.0 &      5.62 &    --1.362 &     33.93 &     21.66 &     16.11 &     32.75 &     10.02 \\
 6155.130 &      14.0 &      5.62 &    --0.786 &     67.36 &     53.11 &     35.29 &     72.00 &     24.98 \\
 6166.440 &      20.0 &      2.52 &    --1.142 &     94.19 &    105.46 &     42.32 &     99.45 &     35.88 \\
 6169.040 &      20.0 &      2.52 &    --0.797 &    112.06 &    120.91 &     66.31 &    120.48 &     55.48 \\
 6169.560 &      20.0 &      2.53 &    --0.478 &    127.89 &    141.16 &     83.69 &    136.37 &     71.35 \\
 6455.600 &      20.0 &      2.52 &    --1.290 &     80.79 &     91.41 &     31.35 &     89.20 &     25.98 \\
 5526.820 &      21.1 &      1.77 &      0.130 &     98.84 &    113.34 &    100.84 &     98.40 &     51.08 \\
 5657.880 &      21.1 &      1.51 &    --0.500 &     96.46 &    107.49 &     92.74 &     95.42 &     41.21 \\
 5667.150 &      21.1 &      1.50 &    --1.240 &     59.41 &     75.04 &     45.00 &     58.54 &     14.51 \\
 5669.040 &      21.1 &      1.50 &    --1.120 &   \nodata &     92.51 &     57.27 &     75.19 &     18.20 \\
 6245.610 &      21.1 &      1.51 &    --0.980 &     67.12 &     83.60 &     53.34 &     67.38 &     14.75 \\
 6604.600 &      21.1 &      1.36 &    --1.480 &     65.58 &     82.06 &     49.37 &     65.92 &     17.81 \\
 6064.630 &      22.0 &      1.05 &    --1.888 &     59.69 &     80.86 &   \nodata &     58.58 &   \nodata \\
 6091.170 &      22.0 &      2.27 &    --0.367 &     45.15 &     59.09 &   \nodata &     56.28 &   \nodata \\
 6312.240 &      22.0 &      1.46 &    --1.496 &     46.16 &     63.41 &   \nodata &     48.78 &   \nodata \\
 6336.100 &      22.0 &      1.44 &    --1.687 &     35.88 &     54.10 &   \nodata &     42.33 &   \nodata \\
 5154.080 &      22.1 &      1.57 &    --1.920 &    112.25 &   \nodata &    114.05 &   \nodata &     53.89 \\
 5185.910 &      22.1 &      1.89 &    --1.350 &   \nodata &    101.45 &    105.46 &   \nodata &     55.30 \\
 5336.790 &      22.1 &      1.58 &    --1.690 &    116.30 &    124.58 &    119.55 &    103.98 &     61.40 \\
 5381.030 &      22.1 &      1.59 &    --2.080 &   \nodata &    131.44 &    101.94 &    109.93 &     47.96 \\
 5727.060 &      23.0 &      1.08 &    --0.010 &    122.36 &   \nodata &     26.00 &    116.79 &      9.13 \\
 6090.220 &      23.0 &      1.08 &    --0.060 &     93.58 &    115.58 &     23.62 &     92.84 &   \nodata \\
 6216.360 &      23.0 &      0.28 &    --1.290 &    108.80 &   \nodata &     16.92 &    109.33 &   \nodata \\
 6251.820 &      23.0 &      0.29 &    --1.340 &     94.66 &    124.37 &   \nodata &     92.43 &   \nodata \\
 6274.640 &      23.0 &      0.27 &    --1.670 &     65.49 &     93.82 &   \nodata &     61.51 &   \nodata \\
 6504.160 &      23.0 &      1.18 &    --1.230 &     22.95 &     33.69 &   \nodata &     31.93 &   \nodata \\
 4545.950 &      24.0 &      0.94 &    --1.370 &   \nodata &   \nodata &     80.22 &   \nodata &   \nodata \\
 4580.056 &      24.0 &      0.94 &    --1.650 &   \nodata &   \nodata &   \nodata &   \nodata &     44.22 \\
 4616.137 &      24.0 &      0.98 &    --1.190 &    128.75 &    139.25 &     89.37 &    126.24 &     59.88 \\
 4626.188 &      24.0 &      0.97 &    --1.320 &    122.24 &    136.41 &     82.24 &   \nodata &     56.90 \\
 4646.150 &      24.0 &      1.03 &    --0.740 &   \nodata &   \nodata &    110.65 &    146.08 &     75.35 \\
 4651.280 &      24.0 &      0.98 &    --1.460 &    127.78 &    140.58 &     75.40 &    116.31 &     48.44 \\
 4652.158 &      24.0 &      1.00 &    --1.030 &    138.48 &   \nodata &     96.92 &    138.00 &     66.74 \\
 5206.040 &      24.0 &      0.94 &      0.020 &   \nodata &   \nodata &   \nodata &   \nodata &    132.81 \\
 5247.564 &      24.0 &      0.96 &    --1.640 &    141.39 &   \nodata &     76.09 &   \nodata &     46.66 \\
 5296.690 &      24.0 &      0.98 &    --1.360 &    149.87 &   \nodata &     85.01 &    140.97 &     59.00 \\
 5300.740 &      24.0 &      0.98 &    --2.000 &    120.48 &   \nodata &   \nodata &    112.22 &   \nodata \\
 5345.800 &      24.0 &      1.00 &    --0.950 &   \nodata &   \nodata &    115.38 &   \nodata &     81.14 \\
 5348.310 &      24.0 &      1.00 &    --1.210 &    150.80 &   \nodata &     94.76 &    142.37 &     63.02 \\
 5409.770 &      24.0 &      1.03 &    --0.670 &   \nodata &   \nodata &    132.36 &   \nodata &     92.13 \\
 4558.594 &      24.1 &      4.07 &    --0.656 &   \nodata &   \nodata &   \nodata &    101.77 &     46.52 \\
 4588.142 &      24.1 &      4.07 &    --0.826 &     46.04 &     52.99 &     60.53 &     55.00 &     35.95 \\
 4591.992 &      24.1 &      4.07 &    --1.419 &   \nodata &   \nodata &     29.08 &     28.53 &     19.56 \\
 6013.530 &      25.0 &      3.07 &    --0.251 &     89.19 &    114.55 &     22.18 &    109.41 &     14.81 \\
 6016.670 &      25.0 &      3.08 &    --0.100 &     93.98 &    116.01 &     28.15 &    113.02 &     17.06 \\
 6021.800 &      25.0 &      3.08 &      0.034 &     97.50 &    116.02 &     39.08 &    110.74 &     19.90 \\
 5044.210 &      26.0 &      2.85 &    --2.034 &   \nodata &   \nodata &   \nodata &   \nodata &     33.70 \\
 5054.640 &      26.0 &      3.64 &    --1.938 &     37.96 &   \nodata &   \nodata &   \nodata &   \nodata \\
 5242.490 &      26.0 &      3.63 &    --0.980 &     94.34 &    101.83 &     72.92 &   \nodata &     49.25 \\
 5321.110 &      26.0 &      4.43 &    --1.106 &     34.97 &     35.32 &     11.14 &   \nodata &   \nodata \\
 5322.040 &      26.0 &      2.28 &    --2.840 &     93.10 &    103.03 &     59.48 &   \nodata &     30.88 \\
 5326.140 &      26.0 &      3.57 &    --2.130 &     40.39 &     51.67 &     13.75 &     48.44 &   \nodata \\
 5365.400 &      26.0 &      3.57 &    --1.040 &   \nodata &    100.31 &   \nodata &     93.75 &   \nodata \\
 5367.480 &      26.0 &      4.41 &      0.430 &    108.42 &    118.03 &     92.35 &    119.08 &     73.73 \\
 5379.570 &      26.0 &      3.69 &    --1.530 &     71.36 &     81.40 &     34.91 &     75.65 &     19.57 \\
 5491.840 &      26.0 &      4.18 &    --2.250 &   \nodata &   \nodata &   \nodata &     17.29 &   \nodata \\
 5618.630 &      26.0 &      4.21 &    --1.292 &     43.46 &     54.27 &     20.25 &     57.44 &     11.30 \\

>>>>

\usepackage{amssymb,graphics} % for resolution symbol
\usepackage{longtable}

@@

% TODO:

% [DONE] Na/O subplots
% [DONE] Na/O comparison with halo
% [DONE] Mg/Al subplots
% - Ni/Na plane plot
% - Add standard stars to observations table
% - Add standard stars chemical abundances
% - Add in-line text referencing standard star chemical abundances
% - Uncertainties analysis
% [DONE] Equivalent widths significant figures.
% - Strontium?
% - Carbon?
% - Distance calculations revision
% - Transverse motions table
% - Transverse motions text
% - Orbital energies plot
% - Minor merger text
% - Conclusions

% Casey, Keller, Alves-Brito, Frebel, Da Costa, Schlaufman, Karakas, Heather, QinQin, Freeman

@@

Wide-field surveys have proved excellent sources for finding stellar streams. Dozens have been identified through photometric selections and matched-filtering techniques, with some to a galactocentric distance of 100\,kpc \citep{belokurov;et-al_2007,drake;et-al_2013}. Indeed, it is clear that a large fraction of the stellar halo has been built up by accretion. However, as \citet{helmi;white_1999} point out, these observing strategies are only successful for identifying streams that are sufficiently distant from the solar neighbourhood. A nearby stream, within $\sim$10\,kpc, will not appear as an over-density, as the stars would be sparsely positioned across the sky. Such substructures would only be detectable by their kinematics, or perhaps precise chemical abundances through a `chemical tagging' approach (e.g. see \citet{freeman;bland-hawthorn_2002}).

% Talk about RAVE
It is therefore necessary to survey solar neighbourhood stars with spectroscopy to reveal any nearby substructures. The RAVE (Radial Velocity Experiment) team began such a survey in 2003 and have observed spectra from over 500,000 stars across 17,000\,deg$^{2}$. As the name hints, the primary goal of RAVE was to obtain radial velocities for the solar neighbourhood and beyond. In an attempt to remain kinematically unbiased, RAVE candidates were selected based only on their apparent magnitude. With the exception of bulge stars, where some photometric cuts were employed, all stars between 9 $<$ I $<$ 13 were observed. Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with sufficient Signal-to-Noise ($S/N$), estimates of stellar parameters have been derived using a $\chi^2$ minimization technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.

@@

We seek to investigate the nature of the Aquarius stream, specifically the recent globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}. We present a detailed analysis for five Aquarius stream candidates from high-resolution, high $S/N$ observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{bernstein;et-al_2003} with the Magellan Clay telescope. Details of the observations and data reduction are outlined in the following section. The data analysis is chronicled in Section \ref{sec:analysis} and a detailed discussion of these results resides in Section \ref{sec:discussion}. In Section \ref{sec:conclusions} we present our conclusions and critical interpretations.

@@

\\ \multicolumn{11}{c}{Standard Stars} \\ \hline \\
HD 41667		& 06:05:03.7 & $-$32:59:36.8	& 2011-03-13	& 1.005	& \dots & \dots & \dots & 314.4	& \dots & 0.8 \\
HD 142948		& 16:00:01.6 & $-$53:51:04.1	& 2011-03-14	& 1.107	& \dots & \dots & \dots & 6.8		& \dots & 0.4 \\

\\ \multicolumn{11}{c}{Program Stars} \\ \hline \\
C2225316-14437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 1.033 & \dots & \dots & 135	 & --168.6	& --156.4 & 0.1 \\
C2306265-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 1.096 & \dots & \dots & 100	 & --240.4	& --221.1 & 0.1 \\
J221821-183424	& 22:18:21.2 & $-$18:34:28.3	& 2011-07-30	& 1.026	& \dots & \dots & 115 	 & --170.2	& --159.5 & 0.1 \\
J223504-152834	& 22:35:04.5 & $-$15:28:34.9	& 2011-07-30	& 1.047	& \dots & \dots & 135	 & --179.0	& --169.7 & 0.1 \\
J223811-104126	& 22:38:11.6 & $-$10:41:29.4	& 2011-07-30	& 1.218	& \dots & \dots & 115	 & --250.1	& --235.7 & 0.1

@@

The most complete sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}. Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional candidate from the original \citet{williams;et-al_2011} sample. The supplementary star, J2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined. All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and X additional standard stars were observed in March 2011. All observations were taken using a 1.0'' slit, providing a spectral resolution of $\mathcal{R} = 28,000$ in the blue arm and $\mathcal{R} = 22,000$ in the red arm. The total exposure times for our program stars varied to ensure a $S/N$ ratio in excess of 100\,pixel$^{-1}$ at 600\,nm.

@@

The white dwarf HR 6141 was observed on X as a telluric standard. The $S/N$ ratio for HR 6141 exceeds that in any of our standard or program stars. Although the atmospheric conditions at Las Campanas Observatory are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify lines that are affected by telluric absorption. Critical transitions necessary for abundance analyses that are affected by the Earth's atmosphere are corrected for telluric absorption.

@@

\subsection{Radial Velocities}
\label{sec:radial-velocities}

The radial velocity for each star was determined in a two-step method. An initial estimate of the radial velocity was ascertained by cross-correlation with a synthetic spectrum of a giant star with $T_{\rm eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}. The observed spectrum was shifted to the pseudo-rest frame using this initial velocity estimate. Velocities found from cross-correlation are typically within 1\,km\,s$^{-1}$ of our final published value.

\begin{figure}[h!]
	\includegraphics[width=\columnwidth]{./figures/line-velocity.pdf}
	\caption{Residual velocities for each absorption line with a well-fitted Gaussian profile after correcting for doppler shift using the initial cross-correlation measurement. The mean residual velocity $-0.75$\,km\,s$^{-1}$ is within the 1-$\sigma$ cross-correlation uncertainty of $\pm0.9$\,km\,s$^{-1}$.}
	\label{fig:line-velocities}
\end{figure}

@@

@@

We list the atomic data and measured equivalent widths for transitions used during this analysis in Table \ref{tab:equivalent-widths}. Saturated lines were excluded by removing measurements with reduced equivalent widths, $\log_{10}{(EW/\lambda)} > -4.5$\, dex. A minimum detectable equivalent width was calculated as a function of wavelength based on the $S/N$, and only lines that exceeded a 3-$\sigma$ detection significance were included. We have verified the approach by comparing our measurements of 156 lines in HD 140283 with the study of \citet{norris;et-al_1996}. We only included measurements in the \citet{norris;et-al_1996} study that were not marked with questionable line quality parameters. Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}. The mean difference is a negligible $-0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present. We note that the scatter may be directly attributed to the observed $S/N$ ratio, as other studies \citep{frebel;et-al_2013} using the same equivalent width measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ratios: $0.20 \pm 0.16$\,m{\AA} with \citet{aoki;et-al_2007} and $0.25 \pm 0.28$\,m{\AA} with \citet{cayrel;et-al_2004} for a spectrum of HD 122563 with $S/N > 300$\,pixel$^{-1}$.

@@

@@

 6300.300 &       8.0 &      0.00 &    --9.717 &      45.4 &      66.9 &      38.5 &      32.8 &      17.9 \\
 6363.780 &       8.0 &      0.02 &   --10.185 &      19.5 &      28.3 &      13.0 &      18.8 &   \nodata \\
 5688.190 &      11.0 &      2.11 &    --0.420 &   \nodata &   \nodata &      49.0 &     131.5 &      38.4 \\
 6154.230 &      11.0 &      2.10 &    --1.530 &      24.1 &      38.9 &   \nodata &      48.5 &   \nodata \\
 6160.750 &      11.0 &      2.10 &    --1.230 &      37.7 &      58.5 &   \nodata &      65.7 &   \nodata \\
 6318.720 &      12.0 &      5.11 &    --1.970 &   \nodata &      47.9 &      14.7 &      62.8 &       8.9 \\
 6319.240 &      12.0 &      5.11 &    --2.220 &      30.8 &   \nodata &       5.5 &   \nodata &   \nodata \\
 6965.410 &      12.0 &      5.75 &    --1.510 &   \nodata &   \nodata &   \nodata &      59.2 &   \nodata \\
 7387.690 &      12.0 &      5.75 &    --0.870 &      51.7 &      56.3 &      24.7 &      76.0 &      24.0 \\
 6696.020 &      13.0 &      3.14 &    --1.340 &      72.8 &      63.6 &      13.0 &   \nodata &   \nodata \\
 6698.670 &      13.0 &      3.14 &    --1.640 &      39.7 &      33.4 &   \nodata &      39.5 &   \nodata \\
 7835.310 &      13.0 &      4.02 &    --0.470 &      47.8 &      38.4 &   \nodata &      55.9 &       5.4 \\
 7836.130 &      13.0 &      4.02 &    --0.310 &      62.8 &      44.7 &   \nodata &      69.1 &      13.2 \\
 5690.430 &      14.0 &      4.93 &    --1.751 &      56.2 &      43.8 &      25.7 &      53.4 &      16.8 \\
 5793.070 &      14.0 &      4.93 &    --1.843 &      46.1 &      39.8 &      19.3 &      48.4 &   \nodata \\
 6125.020 &      14.0 &      5.61 &    --1.506 &      40.9 &      23.4 &      10.9 &      34.7 &   \nodata \\
 6145.010 &      14.0 &      5.62 &    --1.362 &      33.9 &      21.7 &      16.1 &      32.7 &      10.0 \\
 6155.130 &      14.0 &      5.62 &    --0.786 &      67.4 &      53.1 &      35.3 &      72.0 &      25.0 \\
 6166.440 &      20.0 &      2.52 &    --1.142 &      94.2 &     105.5 &      42.3 &      99.5 &      35.9 \\
 6169.040 &      20.0 &      2.52 &    --0.797 &     112.1 &     120.9 &      66.3 &     120.5 &      55.5 \\
 6169.560 &      20.0 &      2.53 &    --0.478 &     127.9 &     141.2 &      83.7 &     136.4 &      71.3 \\
 6455.600 &      20.0 &      2.52 &    --1.290 &      80.8 &      91.4 &      31.4 &      89.2 &      26.0 \\
 5526.820 &      21.1 &      1.77 &      0.130 &      98.8 &     113.3 &     100.8 &      98.4 &      51.1 \\
 5657.880 &      21.1 &      1.51 &    --0.500 &      96.5 &     107.5 &      92.7 &      95.4 &      41.2 \\
 5667.150 &      21.1 &      1.50 &    --1.240 &      59.4 &      75.0 &      45.0 &      58.5 &      14.5 \\
 5669.040 &      21.1 &      1.50 &    --1.120 &   \nodata &      92.5 &      57.3 &      75.2 &      18.2 \\
 6245.610 &      21.1 &      1.51 &    --0.980 &      67.1 &      83.6 &      53.3 &      67.4 &      14.8 \\
 6604.600 &      21.1 &      1.36 &    --1.480 &      65.6 &      82.1 &      49.4 &      65.9 &      17.8 \\
 6064.630 &      22.0 &      1.05 &    --1.888 &      59.7 &      80.9 &   \nodata &      58.6 &   \nodata \\
 6091.170 &      22.0 &      2.27 &    --0.367 &      45.2 &      59.1 &   \nodata &      56.3 &   \nodata \\
 6312.240 &      22.0 &      1.46 &    --1.496 &      46.2 &      63.4 &   \nodata &      48.8 &   \nodata \\
 6336.100 &      22.0 &      1.44 &    --1.687 &      35.9 &      54.1 &   \nodata &      42.3 &   \nodata \\
 5154.080 &      22.1 &      1.57 &    --1.920 &     112.2 &   \nodata &     114.0 &   \nodata &      53.9 \\
 5185.910 &      22.1 &      1.89 &    --1.350 &   \nodata &     101.4 &     105.5 &   \nodata &      55.3 \\
 5336.790 &      22.1 &      1.58 &    --1.690 &     116.3 &     124.6 &     119.5 &     104.0 &      61.4 \\
 5381.030 &      22.1 &      1.59 &    --2.080 &   \nodata &     131.4 &     101.9 &     109.9 &      48.0 \\
 5727.060 &      23.0 &      1.08 &    --0.010 &     122.4 &   \nodata &      26.0 &     116.8 &       9.1 \\
 6090.220 &      23.0 &      1.08 &    --0.060 &      93.6 &     115.6 &      23.6 &      92.8 &   \nodata \\
 6216.360 &      23.0 &      0.28 &    --1.290 &     108.8 &   \nodata &      16.9 &     109.3 &   \nodata \\
 6251.820 &      23.0 &      0.29 &    --1.340 &      94.7 &     124.4 &   \nodata &      92.4 &   \nodata \\
 6274.640 &      23.0 &      0.27 &    --1.670 &      65.5 &      93.8 &   \nodata &      61.5 &   \nodata \\
 6504.160 &      23.0 &      1.18 &    --1.230 &      22.9 &      33.7 &   \nodata &      31.9 &   \nodata \\
 4545.950 &      24.0 &      0.94 &    --1.370 &   \nodata &   \nodata &      80.2 &   \nodata &   \nodata \\
 4580.056 &      24.0 &      0.94 &    --1.650 &   \nodata &   \nodata &   \nodata &   \nodata &      44.2 \\
 4616.137 &      24.0 &      0.98 &    --1.190 &     128.7 &     139.3 &      89.4 &     126.2 &      59.9 \\
 4626.188 &      24.0 &      0.97 &    --1.320 &     122.2 &     136.4 &      82.2 &   \nodata &      56.9 \\
 4646.150 &      24.0 &      1.03 &    --0.740 &   \nodata &   \nodata &     110.6 &     146.1 &      75.3 \\
 4651.280 &      24.0 &      0.98 &    --1.460 &     127.8 &     140.6 &      75.4 &     116.3 &      48.4 \\
 4652.158 &      24.0 &      1.00 &    --1.030 &     138.5 &   \nodata &      96.9 &     138.0 &      66.7 \\
 5206.040 &      24.0 &      0.94 &      0.020 &   \nodata &   \nodata &   \nodata &   \nodata &     132.8 \\
 5247.564 &      24.0 &      0.96 &    --1.640 &     141.4 &   \nodata &      76.1 &   \nodata &      46.7 \\
 5296.690 &      24.0 &      0.98 &    --1.360 &     149.9 &   \nodata &      85.0 &     141.0 &      59.0 \\
 5300.740 &      24.0 &      0.98 &    --2.000 &     120.5 &   \nodata &   \nodata &     112.2 &   \nodata \\
 5345.800 &      24.0 &      1.00 &    --0.950 &   \nodata &   \nodata &     115.4 &   \nodata &      81.1 \\
 5348.310 &      24.0 &      1.00 &    --1.210 &     150.8 &   \nodata &      94.8 &     142.4 &      63.0 \\
 5409.770 &      24.0 &      1.03 &    --0.670 &   \nodata &   \nodata &     132.4 &   \nodata &      92.1 \\
 4558.594 &      24.1 &      4.07 &    --0.656 &   \nodata &   \nodata &   \nodata &     101.8 &      46.5 \\
 4588.142 &      24.1 &      4.07 &    --0.826 &      46.0 &      53.0 &      60.5 &      55.0 &      36.0 \\
 4591.992 &      24.1 &      4.07 &    --1.419 &   \nodata &   \nodata &      29.1 &      28.5 &      19.6 \\
 6013.530 &      25.0 &      3.07 &    --0.251 &      89.2 &     114.6 &      22.2 &     109.4 &      14.8 \\
 6016.670 &      25.0 &      3.08 &    --0.100 &      94.0 &     116.0 &      28.1 &     113.0 &      17.1 \\
 6021.800 &      25.0 &      3.08 &      0.034 &      97.5 &     116.0 &      39.1 &     110.7 &      19.9 \\
 5044.210 &      26.0 &      2.85 &    --2.034 &   \nodata &   \nodata &   \nodata &   \nodata &      33.7 \\
 5054.640 &      26.0 &      3.64 &    --1.938 &      38.0 &   \nodata &   \nodata &   \nodata &   \nodata \\
 5242.490 &      26.0 &      3.63 &    --0.980 &      94.3 &     101.8 &      72.9 &   \nodata &      49.2 \\
 5321.110 &      26.0 &      4.43 &    --1.106 &      35.0 &      35.3 &      11.1 &   \nodata &   \nodata \\
 5322.040 &      26.0 &      2.28 &    --2.840 &      93.1 &     103.0 &      59.5 &   \nodata &      30.9 \\
 5326.140 &      26.0 &      3.57 &    --2.130 &      40.4 &      51.7 &      13.7 &      48.4 &   \nodata \\
 5365.400 &      26.0 &      3.57 &    --1.040 &   \nodata &     100.3 &   \nodata &      93.8 &   \nodata \\
 5367.480 &      26.0 &      4.41 &      0.430 &     108.4 &     118.0 &      92.4 &     119.1 &      73.7 \\
 5379.570 &      26.0 &      3.69 &    --1.530 &      71.4 &      81.4 &      34.9 &      75.6 &      19.6 \\
 5491.840 &      26.0 &      4.18 &    --2.250 &   \nodata &   \nodata &   \nodata &      17.3 &   \nodata \\
 5618.630 &      26.0 &      4.21 &    --1.292 &      43.5 &      54.3 &      20.2 &      57.4 &      11.3 \\
 5701.550 &      26.0 &      2.56 &    --2.216 &     118.5 &     134.8 &      91.8 &     119.5 &      49.5 \\
